Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-10 R/model_fcs_target_markdown.Rmd
Update

```{r}
m1 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
             substrate_depth + seed_density +
             (1 | site/plot) + (1 | botanist_year),
           data = sites, 
           family = gaussian("identity"),
           prior = priors,
           chains = chains,
           iter = iter,
           thin = thin,
           warmup = floor(iter / 2),
           save_pars = save_pars(all = TRUE),
           cores = parallel::detectCores(),
           seed = 123)

m2 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^4 +
            substrate_depth + seed_density +
            sand_ratio:substrate_depth +
            (1 | site/plot) + (1 | botanist_year),
          data = sites, 
          family = gaussian("identity"),
          prior = priors,
          chains = chains,
          iter = iter,
          thin = thin,
          warmup = floor(iter / 2),
          save_pars = save_pars(all = TRUE),
          cores = parallel::detectCores(),
          seed = 123)

m3 <- brm(n ~ (target_type + exposition + sand_ratio + survey_year_fct)^2 +
                 substrate_depth + seed_density +
                 substrate_depth:sand_ratio +
                 seed_density:exposition +
                 target_type:exposition:survey_year_fct +
                 sand_ratio:exposition:survey_year_fct +
                 seed_density:exposition:survey_year_fct +
                 (1 | site/plot) + (1 | botanist_year),
               data = sites, 
               family = gaussian("identity"),
               prior = priors,
               chains = chains,
               iter = iter,
               thin = thin,
               warmup = floor(iter / 2),
               save_pars = save_pars(all = TRUE),
               cores = parallel::detectCores(),
               seed = 123)
```

>>>>

```{r}
load(file = here("data", "processed", "model_fcs_1.Rdata"))
m1
load(file = here("data", "processed", "model_fcs_2.Rdata"))
m2
```
